Communicative reduction in referring expressions in a multi-player negotation game

### 2023-01-26 write-ups/cogsci23_paper/manuscript.Rmd
add model code chunks

author-information: > 
    \author{{\large \bf Morton Ann Gernsbacher (MAG@Macc.Wisc.Edu)} \\ Department of Psychology, 1202 W. Johnson Street \\ Madison, WI 53706 USA
    \AND {\large \bf Sharon J.~Derry (SDJ@Macc.Wisc.Edu)} \\ Department of Educational Psychology, 1025 W. Johnson Street \\ Madison, WI 53706 USA}

@@

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
library(here)
library(tidyverse)
#library(rstanarm)
#library(rstan)
library(tidybayes)
library(viridis)
library(cowplot)
library(lsa)
library(kableExtra)
#rstan_options(auto_write = TRUE)
#options(mc.cores = parallel::detectCores())
#for plotting
theme_set(theme_bw())

@@

@@

examples <- read_rds(here(model_path,"sbert_examples.rds")) |> left_join(include, by=c("game1"="gameId","ref1"="flower","player1"="name","trialNum1"="trialNum")) |> rename(text1=normalized_span) |> left_join(include, by=c("game2"="gameId","ref2"="flower","player2"="name","trialNum2"="trialNum")) |> rename(text2=normalized_span)

@@

@@

```{r 2-col-image, fig.env = "figure*", fig.pos = "h", fig.width=4, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "This image spans both columns. And the caption text is limited to 0.8 of the width of the document."}
#img <- png::readPNG("figs/walrus.png")
#grid::grid.raster(img)
```

```{r image, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."}
#img <- png::readPNG("figs/lab_logo_stanford.png")
#grid::grid.raster(img)
```

>>>>

author-information: > 
    \author{{\large \bf Veronica Boyce (vboyce@stanford.edu)} \\ Department of Psychology, Stanford University
    \AND {\large \bf Michael C. Frank (mcfrank@stanford.edu)} \\ Department of Psychology, Stanford University}

@@

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
library(here)
library(tidyverse)
#library(rstanarm)
#library(rstan)
#library(tidybayes)
library(viridis)
library(cowplot)
#library(lsa)
library(kableExtra)
#rstan_options(auto_write = TRUE)
#options(mc.cores = parallel::detectCores())
#for plotting
theme_set(theme_bw())

@@

```{r, eval=F}
within_game_flower <- flower_all |> 
  filter(game1==game2) |> 
  filter(ref1==ref2) |> 
  filter(later-earlier<3) |> 
  mutate(same_player=ifelse(player1==player2,1,0),
         flower=str_c(color,ref1)) |> 
  select(sim, condition, earlier, same_player, game1, flower )

m_samegame_sameflower <-  stan_lmer(sim ~ condition*earlier*same_player + 
                                      (1|game1)+(1|flower), data=within_game_flower) |> write_rds(here(model_path,"m2.rds"))

read_rds(here(model_path,"m2.rds")) |> 
show_summary_rstan() |> write_rds(here(model_path,"samegame_sameflower_model.rds"))

within_game_between_flower <- flower_all |> 
  filter(game1==game2) |> 
  filter(ref1!=ref2) |> 
  filter(later-earlier<3) |> 
  mutate(same_player=ifelse(player1==player2,1,0)) |> 
  select(sim, condition, earlier, same_player, game1)

m_samegame_diffflower <-  stan_glm(sim ~ condition*earlier*same_player, data=within_game_between_flower) |> write_rds(here(model_path,"m3.rds"))

read_rds(here(model_path,"m3.rds")) |> show_summary_rstan() |> write_rds(here(model_path,"samegame_diffflower_model.rds"))

within_game_between_flower <- flower_all |> 
  filter(game1==game2) |> 
  filter(ref1!=ref2) |> 
  filter(later-earlier<3) |> 
  mutate(same_player=ifelse(player1==player2,1,0)) |> 
  select(sim, condition, earlier, same_player, game1)

m_samegame_diffflower <-  stan_glm(sim ~ condition*earlier*same_player, data=within_game_between_flower) |> write_rds(here(model_path,"m3.rds"))

read_rds(here(model_path,"m3.rds")) |> show_summary_rstan() |> write_rds(here(model_path,"samegame_diffflower_model.rds"))

@@

# note sbert_examples are generated by running sbert process just on include 
examples <- read_rds(here(model_path,"sbert_examples.rds")) |> left_join(include, by=c("game1"="gameId","ref1"="flower","player1"="name","trialNum1"="trialNum")) |> rename(text1=normalized_span) |> left_join(include, by=c("game2"="gameId","ref2"="flower","player2"="name","trialNum2"="trialNum")) |> rename(text2=normalized_span)

@@

```{r, eval=F}
to_end_same_flower <- to_end |> 
  filter(ref1==ref2) |> 
  mutate(same_player=ifelse(player1==player2,1,0),
         flower=str_c(color,ref1)) |> 
  select(sim, condition, earlier, same_player, gameId, flower)

m_to_end_sameflower <-  stan_glm(sim ~ condition*earlier*same_player, data=to_end_same_flower) |> write_rds(here(model_path,"m5.rds"))

read_rds(here(model_path,"m5.rds")) |> show_summary_rstan() |> write_rds(here(model_path,"to_end_sameflower_model.rds"))

to_end_diff_flower <- to_end |> 
  filter(ref1!=ref2) |> 
  mutate(same_player=ifelse(player1==player2,1,0)) |> 
  select(sim, condition, earlier, same_player, gameId)

m_to_end_diffflower <-  stan_glm(sim ~ condition*earlier*same_player, data=to_end_diff_flower) |> write_rds(here(model_path,"m6.rds"))

read_rds(here(model_path,"m6.rds")) |> show_summary_rstan() |> write_rds(here(model_path,"to_end_diffflower_model.rds"))

within_end <- in_end |> 
  filter(seen1=="own" & seen2=="own") |> 
  filter(player1!=player2) |> 
  mutate(same_flower=ifelse(ref1==ref2, 1, 0),
         same_game=ifelse(game1==game2, 1,0)) |> 
  select(sim, condition, same_flower, same_game)

m_within_end <-  stan_glm(sim ~ condition*same_flower*same_game, data=within_end) |> write_rds(here(model_path,"m7.rds"))

read_rds(here(model_path,"m7.rds")) |> show_summary_rstan() |> write_rds(here(model_path,"within_end.rds"))

@@
